Experimenting with n-grams in Civil Procedure Codes

### 2014-08-05 experiment.Rmd
Plot of matches in test codes

---
title: "Experimenting with n-grams in Civil Procedure Codes"
author: "Kellen Funk and Lincoln Mullen"
date: "August 4, 2014"
output: html_document
---

@@

>>>>

---
title: "Experimenting with n-grams in Civil Procedure Codes"
author: "Kellen Funk"
date: "August 4, 2014"
output: html_document
---

@@

Now let's create a density map of where the matching n-grams are in a code. Interesting that the beginning and end of the code have fewer matches.

```{r, fig.height = 3, fig.width = 8}
density_plot_color <- rgb(0.5, 0.5, 0.5, 0.1)
nc_matches <- codes_grams$NC1868.txt %in% cf_ny_nc$matches  
nc_matches %>% 
  plot(type = "h",
       col = density_plot_color,
       ann = FALSE,
       yaxt = "n",
       xaxt = "n")
title("Places in NC 1868 Code with Matches in NY 1850 Code",
      xlab = "Position in code",
      ylab = "")
```

We can do the same thing with the MI 1853 code and find that it's not a very good match to the NY 1850 code. The matches that are there are probably just noise or common legal terms and English phrases.

```{r, fig.height = 3, fig.width = 8}
cf_ny_mi <- compare_codes_by_shared_ngrams(codes_grams$NY1850part2.txt,
                                           codes_grams$MI1853.txt)
mi_matches <- codes_grams$MI1853.txt %in% cf_ny_mi$matches  
mi_matches %>% 
  plot(type = "h",
       col = density_plot_color,
       ann = FALSE,
       yaxt = "n",
       xaxt = "n")
title("Places in MI 1853 Code with Matches in NY 1850 Code",
      xlab = "Position in code",
      ylab = "")
```
